The manageability of pollination networks in an invasion context

### 2017-02-26 paper/draft_2.Rmd
Minor corrections
References to Figure 3. Fix a definition. Put model summary table in the proper place

All of the networks studied had a driver node density *n~D~* between `r round(min(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` and `r round(max(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` (mean `r round(mean(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)`. 
In addition, we found that, when controlling for potential species richness effects, the *n~D~* of invaded communities was smaller to those of non-invaded communities (Figure 3a; Table S5). 
Nevertheless, of the various covariates we explored, the ratio of plant to pollinator showed the strongest relationship with *n~D~* (Table S4). 
Specifically, we found that as the proportion of pollinators increases and the ratio plant/pollinator balances, *n~D~* decreases (all our communities had more pollinators than plants). 
Other coovariates—connectance (link density) and species richness—had a negative and comparatively less important relationship with *n~D~*.

@@

Maximum matching
  ~ A matching with the largest possible matching size *and* matching weight. 
Superior node
  ~ The node at the start of a matched link. From the control perspective, superior nodes make up the chain(s) that propagate the control signal(s) through the network.

>>>>

All of the networks studied had a driver node density *n~D~* between `r round(min(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` and `r round(max(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)` (mean `r round(mean(dplyr::filter(n_driver, type == "weight")$n_dr_p), digits = 2)`; Figure 3a). 
In addition, we found that, when controlling for potential species richness effects, the *n~D~* of invaded communities was smaller to those of non-invaded communities (Figure 3b; Table S5). 
Nevertheless, of the various covariates we explored, the ratio of plant to pollinator showed the strongest relationship with *n~D~* (Table S4; Figure 3c). 
Specifically, we found that as the proportion of pollinators increases and the ratio plant/pollinator balances, *n~D~* decreases (all our communities had more pollinators than plants). 
Other coovariates—connectance (link density) and species richness—had a negative and comparatively less important relationship with *n~D~*.

@@

Maximum matching
  ~ A matching with the largest possible matching size *and* matching weight.

Superior node
  ~ The node at the start of a matched link. From the control perspective, superior nodes make up the chain(s) that propagate the control signal(s) through the network.

### 2017-02-26 paper/supp_info_2.Rmd
Minor corrections
References to Figure 3. Fix a definition. Put model summary table in the proper place

manag_table %>%
	xtable::xtable(caption = "\\textbf{Coefficients of the $n_D$ models}. Estimates are averaged over the models that accounted for 95\\% of the evidence weight.",
										 digits =  c(0, 0, 2, 2, 2),
										 display = c("d", "s", "f", "f", "G")) %>%
	print(booktabs = T, include.rownames = F,  caption.placement = "top", comment = F, sanitize.text.function = function(x){x})

>>>>

manag_table %>%
	xtable::xtable(caption = "\\textbf{Coefficients of the $n_D$ models}. Estimates are averaged over the models that accounted for 95\\% of the evidence weight.",
										 digits =  c(0, 0, 2, 2, 2),
										 display = c("d", "s", "f", "f", "G")) %>%
	print(booktabs = T, include.rownames = F,  caption.placement = "top", comment = F, sanitize.text.function = function(x){x}, table.placement = "H")
